---
output:
  md_document:
    variant: markdown_github
  html_document:
    keep_md: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-images/",
  message = FALSE,
  fig.width = 5,
  fig.height = 4
)
library(ggplot2)
theme_set(theme_bw(base_family = "HiraKakuProN-W3"))
```

# Sparse Gaussian Markov Random Field Mixtures for Anomaly Detection

#### *Koji Makiyama (@hoxo_m)*

## 1 Overview

The **sGMRFmix** package provides an implementation of the algorithm presented by Ide et al. (2016).
It is a novel anomaly detection method for multivariate noisy sensor data.
It can automatically handle multiple operational modes.
And it can also compute variable-wise anomaly scores.

First, we ready a multivariate training data that contains no anomaly observations.
It consists of four parts and repeats two operational modes.

```{r}
library(sGMRFmix)
set.seed(314)
train_data <- generate_train_data()
plot_multivariate_data(train_data)
```

Second, we ready a multivariate test data that contains some anomaly values.
It consists of 500 normal observations and 500 anomaly observations.
The normal part in the test data consists of two operational modes that also have seen in the training data.
Note that the variable `x5` has no difference in the normal and anomaly part.

```{r}
test_data <- generate_test_data()
plot_multivariate_data(test_data)
```

We input the training data to the `sGMRFmix()` function to learn the two operational modes.
Then we compute variable-wise anomaly scores for test data using the result.

```{r cache=TRUE}
fit <- sGMRFmix(train_data, K = 7, rho = 1.1, verbose = FALSE)
anomaly_score <- compute_anomaly_score(fit, test_data)
plot_multivariate_data(anomaly_score) + ylim(0, 30)
```

You can see that anomalies are found in the latter part of the test data.
And you can also see the variable `x5` has no high anomaly scores. 

## 2 Installation

You can install the package from GitHub.

```r
install.packages("devtools") # if you have not installed "devtools" package
devtools::install_github("hoxo-m/sGMRFmix")
```

The source code for **sGMRFmix** package is available on GitHub at

https://github.com/hoxo-m/sGMRFmix.

## 3 Details

## 4 Related Work

## 5 References

- [1] T. Ide, A .Khandelwal, J .Kalagnanam, **Sparse Gaussian Markov Random Field Mixtures for Anomaly Detection**, IEEE 16th International Conference on Data Mining (ICDM), 2016, pp 955–960
